Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2013-11-12 paper/paper.tex
nicer title Tested everything on collins.
small cahnges to python files, cleaned up file_loader a bit Tested everything on node33.

\begin{document}
\title{E Coli Project Paper Incredibly Rough Draft}

@@

Simulations of this shape that has the same height and dimensions .6
times the size do not exhibit the same pattern.  In these the MinD
maxima oscillate quickly back and forth between the two lower corner
poles.

>>>>

\begin{document}
\title{Robustness of MinD oscillation in \emph{Escherichia coli} with
  diverse cell shapes}

@@

Simulations of this shape that has the same height and dimensions .6
times the size (cells roughly $1.6\mu m$ from top to bottom) do not
exhibit the same pattern.  In these the MinD maxima oscillate quickly
back and forth between the two lower corner poles.
